---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
codeclan_tweets <- read_csv("data/code_clan_tweets.csv")
```

```{r}
dim(codeclan_tweets)
```

```{r}
names(codeclan_tweets)

codeclan_tweets
```

Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
filter(codeclan_tweets, is_quote == FALSE) %>% 
  summarise(no_tweets = sum(favorite_count))
```

Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
filter(codeclan_tweets, is_quote == FALSE) %>%
  group_by(source) %>% 
  summarise(mean_of_retweets = mean(retweet_count))
  
```

Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
codeclan_tweets %>%
  mutate(media_type = coalesce(media_type, "text")) %>% 
  group_by(media_type) %>% 
  summarise(no_likes = sum(favorite_count))
```

Find the mean number of characters that a CodeClan tweet contains.

```{r}
codeclan_tweets %>% 
summarise(mean(display_text_width))
```

The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
codeclan_info <- read_csv("data/code_clan_info.csv")

tweets_status_url <- left_join(codeclan_tweets, codeclan_info, by = "tweet_id")
```

From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.

```{r}
codeclan_hashtags <- tweets_status_url %>% 
  select(tweet_id, hashtags) %>% 
  mutate(hashtags = str_to_lower(hashtags)) %>% 
  drop_na()

codeclan_hashtags
```

