---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(modelr)
library(GGally)
library(ggplot2)
```


```{r}
king_county <- read_csv("data/kc_house_data.csv")
glimpse(king_county)
view(king_county)
```

# You might like to think about removing some or all of date, id, sqft_living15, sqft_lot15 and zipcode (lat and long provide a better measure of location in any event).
```{r}
king_county_tidy <- king_county %>% 
  select(-c("date", "id", "sqft_living15", "sqft_lot15", "zipcode"))
king_county_tidy
unique(king_county_tidy$waterfront)
```

Have a think about how to treat waterfront. Should we convert its type?
```{r}
king_county_tidy <- king_county_tidy %>% 
  mutate(waterfront = ifelse(waterfront == "1", TRUE, FALSE))
king_county_tidy
```

We converted yr_renovated into a renovated logical variable, indicating whether the property had ever been renovated. You may wish to do the same.
```{r}
unique(king_county_tidy$yr_renovated)
king_county_tidy <- king_county_tidy %>% 
  mutate(renovated = ifelse(yr_renovated == 0, FALSE, TRUE)) %>% 
  select(-yr_renovated)
king_county_tidy
```


```{r}
unique(king_county_tidy$condition)
unique(king_county_tidy$grade)
```

Check for aliased variables using the alias() function (this takes in a formula object and a data set). [Hint - formula price ~ . says ‘price varying with all predictors’, this is a suitable input to alias()]. Remove variables that lead to an alias. Check the ‘Elements of multiple regression’ lesson for a dropdown containing further information on finding aliased variables in a dataset.

```{r}
alias(lm(price ~ ., data = king_county_tidy))
```

```{r}
king_county_tidy <- king_county_tidy %>% 
  select(-sqft_basement)
```



Systematically build a regression model containing up to four main effects (remember, a main effect is just a single predictor with coefficient), testing the regression diagnostics as you go
```{r}
mod1a <- lm(price ~ sqft_living, data = king_county_tidy)
summary(mod1a)
```

```{r}
par(mfrow = c(2,2))
plot(mod1a)
```

```{r}
mod1b <- lm(price ~ bedrooms, data = king_county_tidy)
summary(mod1b)
```

```{r}
par(mfrow = c(2,2))
plot(mod1b)
```


```{r}
mod1c <- lm(price ~ sqft_lot, data = king_county_tidy)
summary(mod1c)
```
```{r}
par(mfrow = c(2,2))
plot(mod1c)
```



```{r}
mod1d <- lm(price ~ waterfront, data = king_county_tidy)
summary(mod1d)
```
```{r}
par(mfrow = c(2,2))
plot(mod1d)
```


```{r}
mod1e <- lm(price ~ condition, data = king_county_tidy)
summary(mod1e)
```

```{r}
par(mfrow = c(2,2))
plot(mod1e)
```

```{r}
mod1f <- lm(price ~ renovated, data = king_county_tidy)
summary(mod1f)
```
```{r}
par(mfrow = c(2,2))
plot(mod1f)
```

```{r}
mod1g <- lm(price ~ yr_built, data = king_county_tidy)
summary(mod1g)
```
```{r}
par(mfrow = c(2,2))
plot(mod1g)
```

```{r}
mod1h <- lm(price ~ grade, data = king_county_tidy)
summary(mod1h)
```

```{r}
par(mfrow = c(2,2))
plot(mod1h)
```


```{r}
modfinal <- lm(price ~ sqft_living + grade + bedrooms + waterfront, data = king_county_tidy)
summary(modfinal)
```

```{r}
par(mfrow = c(2,2))
plot(modfinal)
```





```{r}
houses_tidy_numeric <- king_county_tidy %>%
  select_if(is.numeric)
houses_tidy_nonnumeric <- king_county_tidy %>%
  select_if(function(x) !is.numeric(x))
houses_tidy_nonnumeric$price <- king_county_tidy$price
ggpairs(houses_tidy_numeric)
ggpairs(houses_tidy_nonnumeric)
```

```{r}
anova(mod1a, mod1h)
```