---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
```
# Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}
CodeClanData::backpack
```

```{r}
head(backpack)
dim(backpack)
names(backpack)
```

# Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_histogram(col = "white")
```
The distribution of the backpack weight is pretty much all in the 0 to 20 kgs with a couple of outliers.


# Question 3.

Are there differences in backpack weight between sex?

```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_histogram(col = "white") +
  facet_wrap(~ sex)
```
The weight of the male bags is slightly more spread out than the females.


# Question 4.

What is the relationship between body weight and backpack weight?

```{r}
ggplot(backpack) +
  aes(x = backpack_weight, y = body_weight) +
  geom_point()
```
I dont see any real discernable pattern.


# Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
ggplot(backpack) +
  aes(x = backpack_weight, y = body_weight, colour = sex) +
  geom_point() +
  facet_wrap(~ sex) +
  theme_classic()
```
Male bodyweights are on average heavier but backpack weights are braodly similar


# Question 6.

What proportion of students report back pain?

```{r}
back_pain <- backpack %>%
  mutate(back_problems = recode(back_problems, 
                       "0" = "No", 
                       "1" = "Yes"))
```
```{r}
ggplot(back_pain) + 
  aes(x = back_problems, fill = back_problems) + 
  geom_bar() +
ylim(0,100) + 
  labs(x = "backpain reported", y = "student count") +
    scale_fill_manual(values=c("#993300", "#996600")) +
theme(legend.position = "none")
```

# Question 7.

Is this proportion different between men and women?

```{r}
ggplot(back_pain) + 
  aes(x = back_problems, fill = back_problems) + 
  geom_bar() +
ylim(0,100) + 
  labs(x = "backpain reported", y = "student count") +
    scale_fill_manual(values=c("#993300", "#996600")) +
  facet_wrap(~ sex) +
theme(legend.position = "none")
```






