---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
library(tidyverse)

titanic <- read.csv("data/titanic.csv")

titanic %>% 
  distinct(class)
```
```{r}
titanic <- titanic %>%
  mutate(crew = class %in% c("engineering crew", "victualling crew", "restaurant staff", "deck crew"))

titanic %>%
  count(crew)
```

```{r}
titanic %>%
  filter(crew) %>%
  summarise(prob = sum(survived == "yes") / n())
```

```{r}
titanic %>%
  filter(!crew) %>%
  summarise(prob = sum(survived == "yes") / n())
```




# 2 MVP and Extension - Probability problems
Today was pretty full-on! Here are some problems to help you consolidate what you learned. Feel free to work on paper or in R, whichever you are most comfortable with:

MVP - try four of the problems
Extension - try more than four!

1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
roll_die_once <- rolldie(1) 

roll_die_once %>% 
  filter(roll_die_once < 5)


```

```{r}
q1 %>%
  filter(X1 < 5)
```


2. How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
three_dice_sample<- rolldie(3) %>% 
  summarise(sample = nrow(rolldie(3)))
three_dice_sample
```


3.  In an experiment where we roll four dice:


```{r}
s_4_dice <- rolldie(4) 
s_4_dice
  
```

i - How many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)?
```{r}
total_equals_5_6_7 <- s_4_dice %>%
  summarise(num_outcomes = rowSums(. == 5|6|7)) %>% 
  head(1)
total_equals_5_6_7
```

ii - What is the probability of this event?

prob(event) = num(event outcomes) / num (all outcomes)

```{r}
s_4_dice_total_outcomes <-  nrow(rolldie(4))
s_4_dice_total_outcomes
prob_total_equals_5_6_7 <- 4 / 1296
prob_total_equals_5_6_7 
```

iii - What assumptions do we apply in answering part ii?

The assumption is that all outcomes are equally likely 

4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

```{r}
group_heights <- c(100, 101, 102, 103, 104)
seats <- as_tibble(
  
  permutations(n = 5,
               r =5,
               v = group_heights,
               repeats.allowed = FALSE)
  
)
seats
ordered_seats <- seats %>% 
  filter(V1 == 104, V2== 103, V3 == 102, V4 == 101, V5 == 100 )
```

```{r}
prob_ordered_seats <- nrow(ordered_seats) / nrow(seats)
prob_ordered_seats
```

Probability is 0.008





